Approximation as Differentiation

### 2025-04-16 appendix/notes/fam.tex
Tweaks.

\begin{definition}[Category of $I$-indexed families of objects]
For any set $I$ and any category $\cat{C}$ write $\Fam(I,\cat{C})$ for the category where:
\begin{itemize}
\item objects are the $I$-indexed families of objects of $\cat{C}$;
\item morphisms from $X$ to $Y$ are families of morphisms $f_i: X_i \to Y_i$ in $\cat{C}$ for any $i \in I$.
\end{itemize}
\end{definition}

@@

\begin{definition}[$\Fam(-,\cat{C})$ functor]
$\Fam(-,\cat{C}): \Set^{\op} \to \Cat$ is then the functor which sends any set $I$ to $\Fam(I,\cat{C})$ and
any function $f: I \to J$ to the functor $\reindex{-}{f}: \Fam(J,\cat{C}) \to \Fam(I,\cat{C})$.
\end{definition}

>>>>

\begin{definition}[Category of $I$-indexed families of objects]
For any set $I$ and any category $\cat{C}$ write $\Fam(I,\cat{C})$ for the category which has:
\begin{itemize}
\item as objects all $I$-indexed families of objects of $\cat{C}$;
\item as morphisms from $X$ to $Y$ all families of morphisms $f_i: X_i \to Y_i$ in $\cat{C}$ for any $i \in
I$.
\end{itemize}
\end{definition}

@@

\begin{definition}
Then define $\Fam(-,\cat{C}): \Set^{\op} \to \Cat$ to be the functor which sends any set $I$ to
$\Fam(I,\cat{C})$ and any function $f: I \to J$ to the functor $\reindex{-}{f}: \Fam(J,\cat{C}) \to
\Fam(I,\cat{C})$.
\end{definition}
